---
title: "USACE MVR Water Quality Monitoring Data"
output:
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: lumen
    orientation: columns
    vertical_layout: scroll
    logo: "Picture1.png"

---

<style>

.navbar-brand {
font-weight:bold;
font-size:25px;
font-stretch:expanded;}

.logo {
  float: left;
}

</style>


```{r}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(crosstalk)
library(anytime)
library(ggplot.multistats)
library(ggplot2)
library(gridExtra)
library(scales)
library(plotly)
library(readr)
library(tidyr)
library(crosstalk)
library(RColorBrewer)
library(bslib)
library(gt)
library(lubridate)
library(feather)

```

```{r}


#Import and rename continuous sd frame
sd <- read.csv("Compiled Project Spreadsheet.csv")
write_feather(sd, "sd.feather")

sd <- read_feather("sd.feather")


#Format Date and Time
sd$Date <- mdy(sd$Date)

sd <- sd %>% 
  mutate(DateTime= as.POSIXct(paste(Date, Time), format= "%Y-%m-%d %H:%M:%S"))

sd$DateTime <- anytime(sd$DateTime) 

#Add DateTime column without year

sd <- sd |> 
  mutate(NEWDATE = format(as.Date(Date, "%y-%m-%d"), "%m-%d"))

sd <- sd %>% 
  mutate(NEWDateTime= as.POSIXct(paste(NEWDATE, Time), format= "%m-%d %H:%M:%S"))

sd$NEWDATE <- anytime(sd$NEWDATE) 

#Subtract year for November and December to plot properly for winter page
sd <- sd |> 
  mutate(FINALDATE = case_when(
    month(NEWDateTime) %in% c(12, 11) ~ NEWDateTime - years(1), TRUE ~ NEWDateTime))
  


#Select parameters of use
sd <- sd %>% 
    select("Site", "Season", "DateTime","FINALDATE", "Temp", "SpCon", "DO", "pH", "Turbidity", "Depth")

#Filter to seperate summer and winter data
sd_winter <- sd |>  
    filter(grepl('Winter', sd$Season)) 

sd_summer <- sd |>  
    filter(grepl('Summer', sd$Season)) 
  
# Wrap sd in Sharedsd to use with crosstalk

sd <- SharedData$new(sd)

sd_winter <- SharedData$new(sd_winter)

sd_summer <- SharedData$new(sd_summer)

```




Summer Data
=======================================================================


Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}

season_filter <- filter_checkbox(
  id = "Season",
  label = "Season(s):",
  sharedData = sd_summer,
  group = ~Season
)

site_filter <- filter_select(
  id =  "Site",
  label = "Site:",
  sharedData = sd_summer,
  group = ~Site, 
)


crosstalk::bscols(
     list(
       season_filter,
       site_filter
      )
)


```

**Monitoring Site Descriptions:**

**W-M329.5Y** - Continuous monitoring and grab samples. Representative location of Upper Bay for future overwintering habitat and dredging.

**W-M329.8P** - Continuous monitoring and grab samples. Representative location of Willow Slough for future overwintering habitat and dredging.


**W-M328.8K** - Grab samples. Representative location of Boater's Chute.

**W-M328.5X** - Grab samples. Representative location of Middle Bay for future overwintering habitat and dredging.


Column {sd-width=550}
-----------------------------------------------------------------------

<font size="5"> **Quincy Bay HREP** </font>

Water quality related goals of the Quincy Bay HREP include restoring diversity of aquatic habitat types with desire for more lentic and backwater habitats and restoring aquatic vegetation in backwater areas.

*Pre-Project Monitoring: 2021-2024*  
*Construction: NA*  
*Post-Monitoring: NA*  

### Continuous Monitoring Data

```{r}
#Plot sd


  DO <- plot_ly(data=sd_summer, 
                x=~FINALDATE, 
                y=~DO, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues"))|> 
        layout(yaxis = list(title = "Dissolved Oxygen (mg/L)"), showlegend=T) |> 
        add_lines()

  Temp <-plot_ly(data=sd_summer, 
                x=~FINALDATE, 
                y=~Temp, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |> 
         layout(yaxis = list(title = "Temperature (C)"), showlegend=F) |> 
         add_lines()
  
  pH <- plot_ly(data=sd_summer, 
                x=~FINALDATE, 
                y=~pH, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |>   
        layout(yaxis = list(title = "pH (none)"), showlegend=F) |> 
        add_lines() 
  
  SpCon <- plot_ly(data=sd_summer, 
                x=~FINALDATE, 
                y=~SpCon, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |> 
          layout(yaxis = list(title = "Specific Conductance (ug/L)"), showlegend=F) |> 
          add_lines()
  
   Turb <- plot_ly(data=sd_summer, 
                x=~FINALDATE, 
                y=~Turbidity, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |> 
          layout(yaxis = list(title = "Turbidity (FNU)"), showlegend=F) |> 
          add_lines()

   
   # Depth <- plot_ly(data=sd, 
   #                  x=~DateTime, 
   #                  y=~Depth)|> 
   #         layout(yaxis = list(title = "Depth (m)")) |> 
   #         add_lines()
  
  
  fig <- subplot(DO, Temp, pH, SpCon, Turb, nrows = 5, titleY = TRUE)
  
##plotly::layout
  
fig
 
```


Column {sd-width=450}
-----------------------------------------------------------------------
    
### Project Site Locations

```{r}

 library(leaflet)
  library(sp)
  
  #Loc <- read.csv("QuincyBay_Locations.csv")
  
  #Loc$Long <- as.numeric(Loc$Long)
  #Loc$Lat <- as.numeric(Loc$Lat)
  
  
  m <- leaflet() %>% 
    addTiles() %>% 
    addCircleMarkers(lng = -91.41439, lat = 39.97359, label = "W-M329.5Y") |> 
    addCircleMarkers(lng = -91.434937, lat = 39.953843, label = "W-M328.8K") |>  
    addCircleMarkers(lng = -91.433622, lat = 39.969817, label = "W-M329.8P") |> 
    addCircleMarkers(lng = -91.421269, lat = 39.9559, label = "W-M328.5X")
  
  m

```

### Boxplot Statistics

```{r}

DO_box <- plot_ly(data=sd_summer, y = ~DO, type = "box", name = "Dissolved Oxygen (mg/L)", color = "#336699" ,colors = "#336699")


Temp_box <- plot_ly(data=sd_summer, y = ~Temp, type = "box", name = "Temperature (C)", color = "#336699", colors = "#336699")
  

pH_box <- plot_ly(data=sd_summer, y = ~pH, type = "box", name = "pH (none)", color = "#336699", colors = "#336699")
  

SpCon_box <- plot_ly(data=sd_summer, y = ~SpCon, type = "box", name = "Specific Conductance (ug/L)",color = "#336699", colors = "#336699")
  
  
Turb_box <- plot_ly(data=sd_summer, y = ~Turbidity, type = "box", name = "Turbidity (FNU)",color = "#336699", colors = "#336699")

#Depth_box <- sd |> plot_ly(y = ~Depth, type = "box", name = "Depth (m)")

  
  fig_box <- subplot(DO_box, Temp_box, pH_box, SpCon_box, Turb_box) |> 
    hide_legend() 

  fig_box


```



Winter Data
=======================================================================


Inputs {.sidebar }
-----------------------------------------------------------------------

```{r}


season_filter <- filter_checkbox(
  id = "Season",
  label = "Season(s):",
  sharedData = sd_winter,
  group = ~Season
)


site_filter <- filter_select(
  id =  "Site",
  label = "Site:",
  sharedData = sd_winter,
  group = ~Site, 
)



div(style = "margin-top: 85px;",
crosstalk::bscols(
     list(
       season_filter,
       site_filter
      ))
)


```


**Monitoring Site Descriptions:**

**W-M329.5Y** - Continuous monitoring and grab samples. Representative location of Upper Bay for future overwintering habitat and dredging.

**W-M329.8P** - Continuous monitoring and grab samples. Representative location of Willow Slough for future overwintering habitat and dredging.


**W-M328.8K** - Grab samples. Representative location of Boater's Chute.

**W-M328.5X** - Grab samples. Representative location of Middle Bay for future overwintering habitat and dredging.


Column {sd-width=550}
-----------------------------------------------------------------------

<font size="5"> **Quincy Bay HREP** </font>

Water quality related goals of the Quincy Bay HREP include restoring diversity of aquatic habitat types with desire for more lentic and backwater habitats and restoring aquatic vegetation in backwater areas.

*Pre-Project Monitoring: 2021-2024*  
*Construction: NA*  
*Post-Monitoring: NA*  

### Continuous Monitoring Data

```{r}
#Plot sd


  DO <- plot_ly(data=sd_winter, 
                x=~FINALDATE, 
                y=~DO, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues"))|> 
        layout(yaxis = list(title = "Dissolved Oxygen (mg/L)")) |> 
        add_lines()

  Temp <-plot_ly(data=sd_winter, 
                x=~FINALDATE, 
                y=~Temp, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |> 
         layout(yaxis = list(title = "Temperature (C)")) |> 
         add_lines()
  
  pH <- plot_ly(data=sd_winter, 
                x=~FINALDATE, 
                y=~pH, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |>   
        layout(yaxis = list(title = "pH (none)")) |> 
        add_lines() 
  
  SpCon <- plot_ly(data=sd_winter, 
                x=~FINALDATE, 
                y=~SpCon, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |> 
          layout(yaxis = list(title = "Specific Conductance (ug/L)")) |> 
          add_lines()
  
   Turb <- plot_ly(data=sd_winter, 
                x=~FINALDATE, 
                y=~Turbidity, 
                linetype = ~Season, 
                color = ~Season, 
                colors = brewer.pal(3, "Blues")) |> 
          layout(yaxis = list(title = "Turbidity (FNU)")) |> 
          add_lines()

   
   # Depth <- plot_ly(data=sd, 
   #                  x=~DateTime, 
   #                  y=~Depth)|> 
   #         layout(yaxis = list(title = "Depth (m)")) |> 
   #         add_lines()
  
  
  fig <- subplot(DO, Temp, pH, SpCon, Turb, nrows = 5, titleY = TRUE) |>
         hide_legend() 
  
fig
 
```


Column {sd-width=450}
-----------------------------------------------------------------------
    
### Site Locations

```{r}
 
library(leaflet)
  library(sp)
  
  #Loc <- read.csv("QuincyBay_Locations.csv")
  
  #Loc$Long <- as.numeric(Loc$Long)
  #Loc$Lat <- as.numeric(Loc$Lat)
  
  
  m <- leaflet() %>% 
    addTiles() %>% 
    addCircleMarkers(lng = -91.41439, lat = 39.97359, label = "W-M329.5Y") |> 
    addCircleMarkers(lng = -91.434937, lat = 39.953843, label = "W-M328.8K") |>  
    addCircleMarkers(lng = -91.433622, lat = 39.969817, label = "W-M329.8P") |> 
    addCircleMarkers(lng = -91.421269, lat = 39.9559, label = "W-M328.5X")
  
  m

```

### Boxplot Statistics

```{r}

DO_box <- plot_ly(data=sd_winter, y = ~DO, type = "box", name = "Dissolved Oxygen (mg/L)", color = "#336699" ,colors = "#336699")


Temp_box <- plot_ly(data=sd_winter, y = ~Temp, type = "box", name = "Temperature (C)", color = "#336699", colors = "#336699")
  

pH_box <- plot_ly(data=sd_winter, y = ~pH, type = "box", name = "pH (none)", color = "#336699", colors = "#336699")
  

SpCon_box <- plot_ly(data=sd_winter, y = ~SpCon, type = "box", name = "Specific Conductance (ug/L)",color = "#336699", colors = "#336699")
  
  
Turb_box <- plot_ly(data=sd_winter, y = ~Turbidity, type = "box", name = "Turbidity (FNU)",color = "#336699", colors = "#336699")

#Depth_box <- sd |> plot_ly(y = ~Depth, type = "box", name = "Depth (m)")

  
  fig_box <- subplot(DO_box, Temp_box, pH_box, SpCon_box, Turb_box) |> 
    hide_legend() 

  fig_box
  



```



Data Summary
=======================================================================



Column {sd-width=100}
-----------------------------------------------------------------------

<font size="5"> **Collection Methods** </font>

Summer monitoring is defined by EC-HQ to be from May through September. A typical summer season occurs from roughly June through September but can vary due to weather and personnel availability. Winter monitoring is defined by EC-HQ from November to April. A typical winter season occurs from roughly December through March but can vary due to weather and personnel availability.

Continuous monitoring data is collected via YSI EXO sondes. Parameters collected on one sonde are specific conductance and temperature (degrees Celsius), dissolved oxygen (mg/L and % saturation), pH, turbidity (FNU), and at times, chlorophyll (ug/L and RFU) and phycocyanin (ug/L and RFU). Readings are programmed to be taken at 1 hour intervals throughout the duration of the monitoring season.


### Data Collected

```{r}
data <- read.csv("Tracking.csv")


data %>%
  gt() %>%
  tab_header(title = "Monitoring Data Summary at Quincy Bay HREP") %>%
  cols_label(Alias = "Site Name", Winter.2023.2024 = "Winter 2023-2024", Summer.2023 = "Summer 2023", Winter.2022.2023 = "Winter 2022-2023", Summer.2022 = "Summer 2022", Winter.2021.2022 = "Winter 2021-2022", Summer.2021 = "Summer 2021", Winter.2020.2021 = "Winter 2020-2021") %>%
  tab_style(
    style = list(cell_fill(color = "#F4F4F4")),
    locations = cells_body(columns = Alias)
  ) |> 
   cols_align(
    align = "center"
  )
 
```

X indicates grab sample data was collected, and O indicates both continuous monitoring and grab sample data was collected at the indicated site
